Preprocess

### 2024-02-21 src/preprocess.Rmd
Finish results
Prep for andy gpt3 results

---
title: "Preprocess"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Richard Wen <richard.wen@unityhealth.to>"
output: html_notebook
---

@@

            "../tmp/healsl_rd1_rapid_gpt3_v1.csv",

@@

            "../tmp/healsl_rd2_rapid_gpt3_v1.csv",
    ) %>% rename(gpt3_icd10 = api_chat_icd),

>>>>

---
title: "Preprocess"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Richard Wen <richard.wen@unityhealth.to>"
---

@@

            "../tmp/healsl_rd1_rapid_gpt3_v2.csv",
            col_select = c("rowid", "cause1_icd10")
        ) %>% mutate(round = 1),

@@

            "../tmp/healsl_rd2_rapid_gpt3_v2.csv",
            col_select = c("rowid", "cause1_icd10")
        ) %>% mutate(round = 2)
    ) %>% rename(gpt3_icd10 = cause1_icd10),
